From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-20 paper.tex
Cosine similarity figure removed gray blur

Our results for a peer-to-peer work scenarios using an approach based on RGB
camera are summarized in table \ref{tab:results} where the \textit{expected} is
the focus of attention that given the state of the system, it is likely to
attract the subject's gaze. In the same manner, the \textit{captured} is the
focus of attention our approach provides and the \textit{real}, the ground truth
of the subject's gaze direction based on manual annotations from two evaluators
with an average reliability of $ \alpha = .89 $\fixme{Is that Cronbach alpha or
Krippendorff's alpha?}.

>>>>

Our results for a peer-to-peer work scenarios using an approach based on RGB
camera are summarized in table \ref{tab:results} where the \textit{expected} is
the focus of attention that given the state of the system, it is likely to
attract the subject's gaze. In the same manner, the \textit{captured} is the
focus of attention our approach provides and the \textit{real}, the ground truth
of the subject's gaze direction based on manual annotations from two evaluators
with an average reliability of $ \alpha = .89 $ computed using Cronbach's alpha.
